### 2022-04-25 manuscript/main.tex
try compiling latex

\section*{Results}
The third factor, density-dependent dispersal, makes small populations less prone to disperse. It is well established empirically (see Fig~\ref{Fig1}) and theoretically that various biological mechanisms, from collective organization to behavioral switches, can prompt organisms in denser populations to disperse more, e.g. in such a way as to escape competition \parencite{matthysen2005density}. The authors demonstrate how this effect induces a link between carrying capacity and invasion speed, both theoretically and in a dispersal experiment on the parasitoid wasp, \emph{Trichogramma chilonis}.\\

@@

\section*{Conflict of interest disclosure}
The authors of this preprint declare that they have no financial conflict of interest with the content of this article. XXX and XXX are recommenders for PCI XXX

>>>>

\section*{Results}
Figure example (see Fig~\ref{Fig1}). \\

\subsection*{Outline}

\begin{itemize}
  \item Intial description: Cohort size, demographics, data types
  \item Basic analysis: Summary statistics, ordinations, permanovas, mantel tests
  \item Exploration of taxonomic profiles + cogscores / brain, cross-sectional. Linear models. \hl{Is this necessary??}
  \item Try HAllA on multivariate data?
  \item Predictive model (RF) - taxonomic profiles + cogscores.
  \item Taxonomic profiles + brain structure
  \item Gene functions + metabolomes
\end{itemize}

@@

\section*{Conflict of interest disclosure}
The authors of this preprint declare that they have no financial conflict of interest with the content of this article. \hl{XXX} and \hl{XXX} are recommenders for PCI \hl{XXX}
